*Prochlorococcus marinus* responses to light and oxygen

### 2024-02-23 Code/Manuscript_O2.Rmd
added PUR estimate figures and captions

>>>>

```{r MED4OverlayPlots, fig.cap = MED4OverlayPlots_cap, fig.height = 6, fig.width = 8, echo = FALSE}

MED4OverlayPlots_cap <- glue("**Normalized absorbance and Photosynthetically Usable Radiation for *Prochlorococcus marinus* MED4 grown under three emission wavebands.**",
                       "**A.** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated absorbed PUR spectra (solid black line and shaded grey).",
                       "**B.** Growth light emission spectra at 660 nm (normalized to 647 nm; dotted red line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated absorbed PUR spectra (solid black line and shaded red).", 
                       "**C.**  Growth light emission spectra at 450 nm (normalized to 441 nm; dotted blue line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated absorbed PUR spectra (solid black line and shaded blue).",

                       "Actinic PAR (µmol photons m^-2^ s^-1^) and calculated absorbed PUR (µmol photons m^-2^ s^-1^) levels are indicated.",

knitr::include_graphics(file.path(FiguresIn, "MED4OverlayPlots.png"))

```{r SS120OverlayPlots, fig.cap = SS120OverlayPlots_cap, fig.height = 6, fig.width = 8, echo = FALSE}

SS120OverlayPlots_cap <- glue("**Normalized absorbance and Photosynthetically Usable Radiation for *Prochlorococcus marinus* SS120 grown under three emission wavebands.",
                       "**A.** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated absorbed PUR spectra (solid black line and shaded grey).",
                       "**B.** Growth light emission spectra at 660 nm (normalized to 647 nm; dotted red line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated absorbed PUR spectra (solid black line and shaded red).",  
                       "**C.**  Growth light emission spectra at 450 nm (normalized to 441 nm; dotted blue line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated absorbed PUR spectra (solid black line and shaded blue).",  
                       "Actinic PAR (µmol photons m^-2^ s^-1^) and calculated absorbed PUR (µmol photons m^-2^ s^-1^) levels are indicated.",
                       .sep = " ")

knitr::include_graphics(file.path(FiguresIn, "SS120OverlayPlots.png"))

```{r MIT9313OverlayPlots, fig.cap = MIT9313OverlayPlots_cap, fig.height = 6, fig.width = 8, echo = FALSE}

MIT9313OverlayPlots_cap <- glue("**Normalized absorbance and Photosynthetically Usable Radiation for *Prochlorococcus marinus* MIT9313 grown under three emission wavebands.**",
                                "**A.** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated absorbed PUR spectra (solid black line and shaded grey).",
                       "**B.** Growth light emission spectra at 660 nm (normalized to 647 nm; dotted red line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated absorbed PUR spectra (solid black line and shaded red).",  
                       "**C.**  Growth light emission spectra at 450 nm (normalized to 441 nm; dotted blue line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated absorbed PUR spectra (solid black line and shaded blue).",  
                       "Actinic PAR (µmol photons m^-2^ s^-1^) and calculated absorbed PUR (µmol photons m^-2^ s^-1^) levels are indicated.",

knitr::include_graphics(file.path(FiguresIn, "MIT9313OverlayPlots.png"))
